Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2016-03-08 manuscript/manuscript.Rnw
add common_latex.tex

% species names
\newcommand{\smonkey}[0]{\textit{A. fusciceps}\xspace}
\newcommand{\cow}[0]{\textit{B. taurus}\xspace}
\newcommand{\dog}[0]{\textit{C. familiaris}\xspace}
\newcommand{\armadillo}[0]{\textit{D. novemcinctus}\xspace}
\newcommand{\horse}[0]{\textit{E. caballus}\xspace}
\newcommand{\elephant}[0]{\textit{L. africana}\xspace}
\newcommand{\human}[0]{\textit{H. sapiens}\xspace}
\newcommand{\opossum}[0]{\textit{M. domestica}\xspace}
\newcommand{\mouse}[0]{\textit{M. musculus}\xspace}
\newcommand{\galili}[0]{\textit{S. galili}\xspace}
\newcommand{\sheep}[0]{\textit{O. aries}\xspace}
\newcommand{\bonobo}[0]{\textit{P. paniscus}\xspace}
\newcommand{\carmeli}[0]{\textit{S. carmeli}\xspace}
\newcommand{\pig}[0]{\textit{S. scrofa}\xspace}

% top 50 gene table explanation. Note that if you modify this, you
% should probably also modify the human table explanation, which is
% slightly different.
\newcommand{\tableexplanation}[2]{The top 50 genes by \ac{FPKM} in #1
  which are not annotated as Mt\_rRNA, Mt\_tRNA, rRNA or whose \human
  ortholog is a housekeeping gene. Gene symbol is the gene symbol or
  Ensembl gene id. Human Symbol is the 1:1 human ortholog or the best
  human alignment when enclosed in parenthesis. Human Name is the HUGO
  name corresponding to the human symbol. A complete list of all genes
  is in \cref{#2}.}

\newcommand{\genetreeexplanation}[1]{Gene tree and heatmap of
  expression of genes related to #1. The gene tree was obtained from
  Ensembl~\cite{Cunningham.ea2015:Ensembl2015} and genes from species
  not included in this study or having expression by \ac{FPKM} less
  than 1 were excluded from the plotted tree. Heatmap cells in white
  are from species where there was no expression of the relevant
  transcript (or a species where that transcript does not apply). The
  species names are abbreviated with the first letter of the genus and
  first two letters of the species (for example, \textit{Homo sapiens}
  is \textit{H.sa.}). Genes with duplicate gene names in the same
  species (or no gene named defined) are listed by the Ensemble gene
  ID.}

>>>>

\input{common_latex}

### 2016-03-08 manuscript/supplemental_material.Rnw
add common_latex.tex

\newcommand{\smonkey}[0]{\textit{A. fusciceps}\xspace}
\newcommand{\cow}[0]{\textit{B. taurus}\xspace}
\newcommand{\dog}[0]{\textit{C. familiaris}\xspace}
\newcommand{\armadillo}[0]{\textit{D. novemcinctus}\xspace}
\newcommand{\horse}[0]{\textit{E. caballus}\xspace}
\newcommand{\elephant}[0]{\textit{L. africana}\xspace}
\newcommand{\human}[0]{\textit{H. sapiens}\xspace}
\newcommand{\opossum}[0]{\textit{M. domestica}\xspace}
\newcommand{\mouse}[0]{\textit{M. musculus}\xspace}
\newcommand{\galili}[0]{\textit{S. galili}\xspace}
\newcommand{\sheep}[0]{\textit{O. aries}\xspace}
\newcommand{\bonobo}[0]{\textit{P. paniscus}\xspace}
\newcommand{\carmeli}[0]{\textit{S. carmeli}\xspace}
\newcommand{\pig}[0]{\textit{S. scrofa}\xspace}

\newcommand{\genetreeexplanation}[1]{Gene tree and heatmap of
  expression of genes related to #1. The gene tree was obtained from
  Ensembl~\cite{Cunningham.ea2015:Ensembl2015} and genes from species
  not included in this study or having expression by FPKM less
  than 1 were excluded from the plotted tree. Heatmap cells in grey
  are from species where there was no expression of the relevant
  transcript (or a species where that transcript does not apply).}

>>>>

\input{common_latex}
